InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-30 paper.tex
add cmd line interface and google collab description

\cite{radford2019language} try to avoid this problem in a simple two step procedure:

@@

>>>>

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:

@@

For ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator. It is also possible to enter multiple processors for one pipeline that are then stacked and applied together on the images.

The resulting pipelines especially for the images were hardware expensive and could not be runn efficiently on our own machines. We chose to use the free google collab recources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time.
